---
title: "NARC-2"
format: html
---

## Overview

NARC 2 is the second HF station on your left as you enter the station.

### Equipment summary

- FlexRadio Flex 6400M (HF + 6m) transceiver
    - Astron RS-35A power supply
- Clipper PTT footswitch

- Dell PC, dual monitor set-up

- Elecraft KPA1500 amplifier
  - Elecraft power supply
  
### Connection scheme

```{mermaid}
%%| fig-width: 6.5
%%| fig-label: fig-narc2-connections
%%| fig-cap: "Connection diagram for NARC2"
flowchart TD
  A[Flex 6400M] ---|Coax-Ant1|B[KPA-1500 Ant 1]
  B ---|50A PowerPole|T[Elecraft Power Supply]
  T ---|220V AC|U(220V outlet)
  J ---|120V AC|V(110V outlet)
  A ---|Cat 6|L
  A ---|Tx1 RCA Rem|B
  A --> N(Clipper footswitch)
  A ---|RCA|Q(Relay)
  Q --- R(Kasa Switch)
  R --- J
  A ---|USB|C[NARC2 PC]
  C ---|USB|F(Keyboard)
  C ---|Bluetooth|G(Mouse)
  C ---|HDMI|H(Monitor)
  C ---|CAT 6|L(Network Switch)
  C ---|USB|P(FlexControl Knob)
  J ---|AC Power|C
  E ---|120V AC|I(Kasa Switch)
  I ---|AC Power|J[Surge Protector]
  I ---|Wifi|K(NARC wifi)
  A ---|Power Cable|E[Astron RS-35A]
  B ---|Coax Ant1|D(Antenna Connectors)
  H ---|AC Power|J
```
   
### Software summary

::: {.callout-note}

These sections are generated by parsing a CSV data file in `include/csv/software_versions.csv`.

The code is hidden in the output for aesthetic reasons, but may be revealed by examining the source code file.

:::

```{r}
#| echo: false
software_versions <- readr::read_csv("include/csv/software_versions.csv", show_col_types = FALSE)

narc2 <- software_versions |>
  dplyr::filter(station == 'narc2')
```

#### Operating System

```{r}
#| echo: false
narc2 |>
  dplyr::filter(type == "os") |>
  dplyr::select(software, version, date) |>
  knitr::kable(format = "html") 
```

#### Digital modes

```{r}
#| echo: false
narc2 |>
  dplyr::filter(type == "digital") |>
  dplyr::select(software, version, date) |>
  knitr::kable(format = "html") 
```

#### Logging

```{r}
#| echo: false
narc2 |>
  dplyr::filter(type == "logging") |>
  dplyr::select(software, version) |>
  knitr::kable(format = "html") 
```

#### Remote Control

```{r}
#| echo: false
narc2 |>
  dplyr::filter(type == "remote") |>
  dplyr::select(software, version, date) |>
  knitr::kable(format = "html") 
```

### Operating Guide

The operating guide for the Flex 6400M is [here](flex-6400M.qmd)
