---
title: "Test Suites"
---

This chapter describes the suite of tests that we use to make sure that our stations remain in good operating condition.

## Monthly

W3TM tries and usually succeeds in running these steps on both NARC1 and NARC2 once a month.
The results of the tests are captured in a Google doc located [here](https://docs.google.com/document/d/1yz_meW9ClsBc88PyoOBWdVERrryEH91LUFfP03dS5sA/edit?usp=sharing).
When software versions change, these get updated in [this](https://docs.google.com/spreadsheets/d/1NqblEGvrP0aiqWkBTs1G_hA3oWTKcxh_-Kb_m7E4G70/edit?usp=sharing) Google sheet.
Data from the Google sheet are imported when this site is updated.

### Power-up

- Connect rig to a suitable antenna or dummy load
- Power-up the Astron power supply
- Power-up the rig
- Log-on to the computer using the appropriate user name and password

### Phone operations

- Set power to 100 W or less
- Call CQ or answer a CQ
  - On the IC-7610, use Icom SM-30 desk mic with embedded push-to-talk (PTT) switch or the footswitch.
  - On the Flex 6400M, use the Yaesu mic or headset with the footswitch for PTT.
  
### Logging programs

#### Amateur Contact Log (N3FJP)

- Check <https://www.n3fjp.com/> to determine latest version of software.
- Download and install if there is an update.
- Record the new version [here](https://docs.google.com/spreadsheets/d/1NqblEGvrP0aiqWkBTs1G_hA3oWTKcxh_-Kb_m7E4G70/edit?usp=sharing)
- Open Amateur Contact Log; a shortcut is on the PC desktop
- Confirm version and record it.
- Confirm that ACL tracks of frequency changes & mode changes
- Close application

#### N1MM+

- Start-up N1MM+; update if prompted
- Confirm version
- Confirm that N1MM+ follows frequency changes.
- Close N1MM+.

### Digital mode operations

#### WSJT-X

- Open WSJT-X
- Confirm version matches one recorded [here](https://docs.google.com/spreadsheets/d/1NqblEGvrP0aiqWkBTs1G_hA3oWTKcxh_-Kb_m7E4G70/edit?usp=sharing).
- Select W3YA configuration
- Test WSJT-X receive
- Switch to suitable band for antenna from within WSTJ-X application
- Confirm that rig follows software band change
- Turn RF power to 10 W
- Test WSJT-X CQ transmit
  - Click Enable Tx button
  - Permit 3 xmit cycles
  - If no one responds to CQ, check <https://pskreporter.info>
- If not checking JTAlert, Close WSJT-X.

#### JTAlert, <https://hamapps.com/JTAlert/>

- Check application site, update as needed.
- Open JTAlert
- Confirm version.
- Confirm that received CQs appear in green in JTAlert window
- Test xmit from JTAlert
  - Click on green CQ button to initiate QSO
- Close JTAlert

::: {.callout-note}

TODO: More complete steps

:::

#### JS8Call

- Open JS8Call
- Confirm version matches one recorded [here](https://docs.google.com/spreadsheets/d/1NqblEGvrP0aiqWkBTs1G_hA3oWTKcxh_- Select W3YA configuration
- Test JS8Call receive
- Switch to suitable band for antenna (most JS8Call activity is on 40 m)
- Confirm rig follows software band change
- Confirm RF power is 10 W
-   Test JS8Call heartbeat transmit

::: {.callout-note}

TODO: Complete steps

:::

- If stations respond to heartbeat, all is well.
- Check pskreporter.info to confirm: W3YA _____ was/______ was not heard.
- Close JS8Call

#### Fldigi, <http://www.w1hkj.com/>

- Check site and update fldigi, flrig, or other applications, as needed
- Open fldigi
- Confirm versions matche those recorded [here](https://docs.google.com/spreadsheets/d/1NqblEGvrP0aiqWkBTs1G_hA3oWTKcxh_- On IC-7610, confirm that flrig opens and shows current operating frequency

::: {.callout-tip}
### Operating parameters for IC-7610:

These parameters are for flrig control of the IC-7610.

*Rig*: IC-7610</br>
*COM3*</br>
*Baud*: 38400</br>
*Stop bits*: 1 stop bit</br>
*CI-V*: 0x98
:::

::: {.callout-tip}
### Operating parameters for Flex-6400M

TODO: Add these.

:::

- 7.070 MHz is a watering hole for PSK31 activity on 40m. You might look there to test receive and transmit.
- Check transmit
    - Create test message (e.g., “de w3ya w3ya testing testing”)
    - Transmit message
- Wait 1-2 mins and check pskreporter.info: W3YA _____ was/______ was not heard.
- Close flrig and fldigi.

#### Winlink Express/VARA

- Open Winlink Express
- Update forms and software if prompted
- Confirm Winlink (not forms) version.
- Select Telnet Winlink session and open session, then start the session to retrieve any messages.
- If connection succeeds, send test message to W3TM@winlink.org.
- Select Vara HF Winlink session
- If prompted, update VARA HF
  - Download
  - Install (as administrator)
- Confirm VARA HF version.
- Select an HF target station
- When the channel is clear, start the session
- Close Winlink Express/VARA

#### VarAC

- Open VarAC
- Confirm that VARA HF opens along with VarAC window.
- Confirm verson.
- Use VarAC window to confirm that rig follows band/freq changes.
- Test transmit
- Confirm rig RF power is 10 W
- Transmit beacon
- Wait 1-2 mins then check pskreporter.info: W3YA _____ was/______ was not heard

#### YONIQ (SSTV)

- Open YONIQ
- Tune to SSTV frequency (e.g., 14.230 MHz)

::: {.callout-note}
TODO: Finish test suite
:::

### Remote

#### Win4IcomSuite

- NARC1/IC-7610 station only
- Open Win4Icom
- Confirm program tracks frequency and mode
- Close Win4Icom

#### wfview

- NARC1/IC-7610 station only
- Open wfview
- Confirm program tracks frequency and mode
- Close wfview

#### SmartSDR

- Open SmartSDR

### KPA1500 Amplifier

- Power on amplifier
- Test ATU
  - Rig to 10% power (~10W). Press MULTI knob(press RF POWER and rotate MULTI knob to read HF 10%)
  - Rig mode to RTTY (touch mode on touchscreen, select RTTY)
  - Amp in standby mode (short press on MODE/PF1) button until yellow STDBY  indicator illuminates
  - Amp to ATU mode (short press on ATU TUNE button)
  - Transmit (press TRANSMIT on rig or PTT on mic to send RF)
  - When ATU cycle ends (after a few seconds), Press TRANSMIT again to end test transmission.
- Test amplification
  - Set amp to operate (short press on OPER/STDBY)
  - Transmit (press TRANSMIT or PTT on mic) on rig 
  - **NOTE** ~10 W drive should generate about 4-500 W out)
  - Press TRANSMIT again to end test transmission
  - Set amplifier back to stand-by (short press on MODE/PF1)
- Power down amplifier
- Return rig to SSB mode (press mode indicator on touch screen, select SSB)

## Maintenance Log

This section downloads information about the latest maintenance activities.
W3TM created a new Google sheet to summarize this information on 2024-11-27.

### Set-up

Here is a link to the [Google Sheet](https://docs.google.com/spreadsheets/d/1h4YUfq1UKwzU8MBJOeOxYSXyhnX518sDBoJ3o-CFqYc/edit?usp=sharing) that W3TM maintains for tracking software version updates.
The following code downloads that file.

```{r}
#| echo: false
#| label: download-narc-maintenance-log
#| message: false

if (!dir.exists('include/csv')) {
  message("Creating missing `include/csv/`.")
  dir.create("include/csv")
}

options(gargle_oauth_email = Sys.getenv("GMAIL_SURVEY"))
googledrive::drive_auth()

googledrive::drive_download(
  "narc-mountaintop-station-maintenance-log",
  path = file.path("include/csv", "maintenance_log.csv"),
  type = "csv",
  overwrite = TRUE
  
)
```

Then, we import the downloaded data.

```{r}
#| echo: false
maintenance_log <- readr::read_csv("include/csv/maintenance_log.csv", show_col_types = FALSE)
```

### Summarize

```{r}
#| echo: false
#| label: tbl-maintenance-log
maintenance_log |>
  dplyr::mutate(comment = ifelse(is.na(comment), "", comment)) |>
  dplyr::select(-callsign) |>
  dplyr::arrange(desc(date), equipment) |>
  knitr::kable(format = "html") |>
  kableExtra::kable_classic()
```


## Contest/Field Day

### Test networked logging

- Rig1 in phone mode, log contact
- Rig2 in phone mode, log contact
- Change Rig1 band
- Change Rig2 band
- Change Rig1 to CW, log contact
- Change Rig2 to CW, log contact
- For each digital mode that will be used...
  - On Rig1, open digital app, attempt to make contact and log it
  - On Rig2, open digital app, attempt to make contact and log it
- Close all apps
- Check log file
